---
title: $\color{#E31A1C}{\text{Belkin}}$ vs. $\color{#6A3D9A}{\text{Elago}}$
subtitle: 'Exploratory Data Analysis'
author: "Murilo Miranda"
date: "`r format(Sys.Date(), '%Y-%B-%d')`"
output:
  html_document:
    toc: true # table of content true
    toc_float: true
    code_folding: hide
    toc_depth: 3  # upto three depths of headings (specified by #, ## and ###)
    theme: united
    highlight: breezedark  # specifies the syntax highlighting style
    #css: styles.css
  pdf_document: default
version: '0.3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=TRUE)

library(summarytools)
st_options(plain.ascii   = FALSE,       # One of the essential settings
           style         = "rmarkdown", # Idem.
           dfSummary.silent  = TRUE,# Suppresses messages about temporary files
           footnote      = NA,          # Keeping the results minimalistic
           subtitle.emphasis = FALSE)   # For the vignette theme, this gives
                                            # much better results. Your mileage may vary.

st_css()
```

```{r, message = FALSE}
library(sjPlot)
library(forcats)
library(dplyr)
library(ggplot2)
library(RColorBrewer)
```


```{r, message = FALSE, echo=FALSE}
colors <- brewer.pal(12, "Paired")
```

# Loading data
The data has empty values and the columns are separated by semicolon. **read.csv2** function was used because it has semi-colon as default sep-argument. To solve the problem with empty values, na.strings argument was used with empty value and single space.

```{r, echo=FALSE}
data <- read.csv2("data/surveyBelkinElago.csv", na.strings = c("", " "))

str(data)
```

# Preprocessing
## Check data types
In the data-set elevel, car and zipcode are integers. In reality, they are categorical variables, so they are converted into factor. The missing values are converted into 'No Response'.

## Data conversions
```{r, echo=FALSE}
data$elevel <- as.factor(data$elevel)
levels(data$elevel) <- c("HSch", "Prof", "Coll", "Mast")
data$elevel <- reorder(data$elevel, data$elevel, FUN = function(x) -length(x))

data$car <- as.factor(data$car)
levels(data$car) <- c("BMW", "Tesl", "Volk", "Fiat", "Chry", "Cit1", "Ford", "Hond", "Opel", "Cit2", "Pors", "Peug", "Audi", "Merc", "Kia", "Niss", "Hyun", "Rena", "Toyo", "Daci")
data$car <- reorder(data$car, data$car, FUN = function(x) -length(x))

data$zipcode <- as.factor(data$zipcode)
levels(data$zipcode) <- c("C", "EC", "E", "NE", "N", "NW", "SE", "SW", "W")
data$zipcode <- reorder(data$zipcode, data$zipcode, FUN = function(x) -length(x))

# convert NA to 'No Response' in the brand variable
levels(data$brand) <- c(levels(data$brand), "No Response")
data$brand[is.na(data$brand)] <- "No Response" 
data$brand <- factor(data$brand, levels = c("No Response", "Belkin", "Elago"))

head(data)
```

## Check duplicate observations
```{r, echo=FALSE}
anyDuplicated(data)
```

## Correlation between variables
```{r, echo=FALSE}
cor(data[, c("salary","age","credit")])
```

### Are missing values at random?
A method I use is a shadow matrix, in which the data-set consists of indicator features where a 0 is given if a value is present, and 1 if it isn't. Correlating these with each other and the original data can help determine if features tend to be missing together (missing at random - MAR) or not (missing completely at random - MCAR). 

```{r, echo=FALSE}
# Elements of x are 1 if a value in the data is missing and 0 if non-missing.
x <- as.data.frame(abs(data$brand == "No Response"))

# Extracting features that have some missing values.
y <- x[which(sapply(x, sd) > 0)]
colnames(y) <- "No Response"
```

I selected the features with numerical values, then their correlations were verified.
```{r, echo=FALSE}
cor(data[, c("salary","age","credit")], y, use="pairwise.complete.obs")
```

```{r, echo=FALSE}
rm(x, y)
```

The correlations shows that they are missing at random.

## Distributions of the variables

```{r, echo=FALSE, results='asis'}
dfSummary(data, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")
```

# Remove **No Response** observations in brand variable
```{r, echo=FALSE}
dataSet <- data %>% filter(brand != "No Response") %>% droplevels()
```

## Comparing some variables with and without **No Response**
```{r table, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
require(kableExtra)

dt <- data.frame(rbind(
  salary = c(19583, 161748, 87244, 20000, 150000, 84969),
  age    = c(20   ,   80  ,   50 ,  20  ,   80  ,   50),
  credit = c(423.7,  849.0, 638.9, 423.7,  849.0,  635.5)))
colnames(dt) <- c("Min", "Max", "Median", "Min", "Max", "Median")

kable(dt) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  add_header_above(c(" " = 1, "With 'No Response'" = 3, "Without 'No Response'" = 3))
```

## Correlation
```{r, echo=FALSE}
cor(dataSet[, c("salary","age","credit")])
```

## Distributions of the variables

```{r, echo=FALSE, results='asis'}
dfSummary(dataSet, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")
```

# Results

```{r, echo=FALSE}
hgram <- ggplot(dataSet, aes(salary, fill = brand)) + geom_histogram(bins = 100) +
  scale_fill_manual(values = c(colors[6], colors[10])) +
  geom_vline(aes(xintercept = median(data$salary)), linetype = "dashed") +
  labs(
    x = "",
    y = "",
    title = "Salary distribution by brand preference",
    subtitle = "Salaries are expressed in yearly thousands of euros",
    caption = "Data source: Ubiqum 2019"
  ) +
  geom_text(x = 80000, y = 70, label = "Belkin", color = "white") +
  geom_text(x = 40000, y = 30, label = "Elago", color = "white")
 
hgram + theme(panel.background = element_rect(fill = "white", colour = "white"),
              plot.title = element_text(hjust = -0.15),
              plot.subtitle = element_text(hjust = -0.17),
              legend.position = "none")
```

```{r, echo=FALSE}
hgram <- ggplot(dataSet, aes(age, fill = brand)) + geom_histogram(bins = 31) +
  scale_fill_manual(values = c(colors[6], colors[10])) +
  geom_vline(aes(xintercept = median(dataSet$age)), linetype = "dashed") +
  labs(
    x = "",
    y = "",
    title = "Age distribution by brand preference",
    subtitle = " ",
    caption = "Data source: Ubiqum 2019"
  ) +
  geom_text(x = 65, y = 220, label = "Belkin", color = "white") +
  geom_text(x = 30, y = 100, label = "Elago", color = "white")
 
hgram + theme(panel.background = element_rect(fill = "white", colour = "white"),
              plot.title = element_text(hjust = -0.15),
              plot.subtitle = element_text(hjust = -0.17),
              legend.position = "none")
```

## Model Hypothesis Testing

The null hypothesis ($H_0$): age and educational level don't affect salary, and the alternative hypothesis ($H_1$): age or educational level  do affect the salary amount.

```{r, echo=FALSE}
model <- lm(salary ~ age + elevel, data = dataSet)

tab_model(
  model,
  pred.labels = c("Intercept", "Age", "College Degree", "High School Degree", "Master's Degree"),
  string.ci = "Conf. Int (95%)",
  string.p = "P-Value"
)
```

<br>
```{r, echo=FALSE}
global_labeller <- labeller(
  elevel = c(`HSch` = "< High School\nDegree", `Prof` = "Professional\nDiploma", `Coll` = "College\nDegree", `Mast` = ">= Master's\nDegree"),
  brand = c(`Belkin` = "", `Elago` = "")
)

dataSet %>%
  mutate(elevel = fct_reorder(elevel, salary, .fun='median')) %>%
  ggplot(aes(x = age, y = salary, color = brand)) + geom_point() + 
  scale_color_manual(values = c(colors[6], colors[10])) + 
  scale_x_continuous(limits = c(20, 80), breaks = c(20, 50, 80), expand = c(0.1, 0.1)) +
  labs(
    x = "",
    y = "",
    title = "Salary distribution by educational level and age separated by brand preference",
    subtitle = "High educational level helps to earn more, age doesn't",
    caption = "Data source: Ubiqum 2019"
  ) +
  facet_grid(. ~ brand + elevel, labeller = global_labeller) + 
  theme(panel.background = element_rect(fill = "white", colour = "white"),
        strip.background = element_blank(),
        plot.title = element_text(hjust = -15.),
        plot.subtitle = element_text(hjust = -.25),
        legend.position = "none")
```

# Conclusion

Age and salary are uniformly distributed and credit is normally distributed. Salary and credit have a high correlation ($\rho$ = 0.795). They are also correlated with educational level, that is, people with a high level of education receive high salary and credit in banks and people with a low level of education receive low salary and credit.

There are more people with **Professional Diploma**, followed by **College Degree**, **High School Degree or lower**, finnally, **Master's Degree or Higher**. Age at educational level is equally distributed.

Older people and people with intermediate income are associated with the $\color{#E31A1C}{\text{Belkin}}$ brand and younger people and people with low or high income are associated with the $\color{#6A3D9A}{\text{Elago}}$ brand.

<br>
