---
title: 'Belkin vs. Elago'
subtitle: 'Exploratory Data Analysis'
author: "Murilo Miranda"
date: "`r format(Sys.Date(), '%Y-%B-%d')`"
output:
  html_document:
    toc: true # table of content true
    toc_depth: 3  # upto three depths of headings (specified by #, ## and ###)
    theme: united  # many options for theme, this one is my favorite.
    highlight: tango  # specifies the syntax highlighting style
  pdf_document: default
version: '0.2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=TRUE)

library(summarytools)
st_options(plain.ascii   = FALSE,       # One of the essential settings
           style         = "rmarkdown", # Idem.
           dfSummary.silent  = TRUE,# Suppresses messages about temporary files
           footnote      = NA,          # Keeping the results minimalistic
           subtitle.emphasis = FALSE)   # For the vignette theme, this gives
                                            # much better results. Your mileage may vary.

st_css()
```

```{r, message = FALSE, echo=FALSE}
library(dplyr)
library(ggplot2)
library(RColorBrewer)
```

# Loading data
The data has empty values and the columns are separated by semicolon. **read.csv2** function was used because it has semi-colon as default sep-argument. To solve the problem with empty values, na.strings argument was used with empty value and single space.

```{r, echo=FALSE}
data <- read.csv2("surveyBelkinElago.csv", na.strings = c("", " "))

str(data)
```

# Preprocessing
## Check data types
In the data-set elevel, car and zipcode are integers. In reality, they are categorical variables, so they are converted into factor. The missing values are converted into 'No Response'.

## Data conversions
```{r, echo=FALSE}
data$elevel <- as.factor(data$elevel)
data$car <- as.factor(data$car)
data$zipcode <- as.factor(data$zipcode)

# convert NA to 'No Response' in the brand variable
levels(data$brand) <- c(levels(data$brand), "No Response")
data$brand[is.na(data$brand)] <- "No Response" 
data$brand <- factor(data$brand, levels = c("No Response", "Belkin", "Elago"))
str(data)
```

## Check duplicate observations
```{r, echo=FALSE}
anyDuplicated(data)
```

## Correlation between variables
```{r, echo=FALSE}
cor(data[, c("salary","age","credit")])
```

### Are missing values at random?
A method I use is a shadow matrix, in which the data-set consists of indicator features where a 0 is given if a value is present, and 1 if it isn't. Correlating these with each other and the original data can help determine if features tend to be missing together (missing at random - MAR) or not (missing completely at random - MCAR). 

```{r, echo=FALSE}
# Elements of x are 1 if a value in the data is missing and 0 if non-missing.
x <- as.data.frame(abs(data$brand == "No Response"))

# Extracting features that have some missing values.
y <- x[which(sapply(x, sd) > 0)]
colnames(y) <- "No Response"
```

I selected the features with numerical values, then their correlations were verified.
```{r, echo=FALSE}
cor(data[, c("salary","age","credit")], y, use="pairwise.complete.obs")
```

```{r, echo=FALSE}
rm(x, y)
```

The correlations shows that they are missing at random.

# Distributions of the variables

```{r, echo=FALSE, results='asis'}
dfSummary(data, plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")
```

```{r, message=FALSE, echo=FALSE}
ggplot(data, aes(age)) + geom_histogram(bins = 35)
```

```{r, echo=FALSE}
p <- ggplot(data, aes(salary, credit)) + geom_point()
ggExtra::ggMarginal(p, type = "histogram")
```

```{r, echo=FALSE}
ggplot(data, aes(elevel, salary)) + geom_boxplot()
```

```{r, echo=FALSE}
ggplot(data, aes(elevel, credit)) + geom_boxplot()
```

```{r, echo=FALSE}
ggplot(data, aes(zipcode, salary)) + geom_boxplot()
```

```{r, echo=FALSE}
ggplot(data, aes(zipcode, credit)) + geom_boxplot()
```

```{r, echo=FALSE}
ggplot(data, aes(car, salary)) + geom_boxplot()
```

```{r, echo=FALSE}
ggplot(data, aes(car, credit)) + geom_boxplot()
```

## Salary distribution by brand preference

```{r, echo=FALSE}
colors <- brewer.pal(12, "Paired")
```


```{r, echo=FALSE}
hgram <- ggplot(data, aes(salary, fill = brand)) + geom_histogram(bins = 100) +
  scale_fill_manual(values = c(colors[8], colors[6], colors[10])) +
  geom_vline(aes(xintercept = median(data$salary)), linetype = "dashed") +
  labs(
    x = "",
    y = "",
    title = "Salary distribution by brand preference",
    subtitle = "Salaries are expressed in yearly thousands of euros",
    caption = "NATU 2019"
  ) +
  geom_text(x = 120000, y = 210, label = "No Response", color = colors[8]) + 
  geom_text(x = 160000, y = 160, label = "Belkin", color = colors[6]) +
  geom_text(x = 160000, y = 100, label = "Elago", color = colors[10])
 
hgram + theme(panel.background = element_rect(fill = "white", colour = "white"),
              plot.title = element_text(hjust = -0.15),
              plot.subtitle = element_text(hjust = -0.17),
              legend.position = "none")
```



# Remove **No Response** observations in brand variable
```{r, echo=FALSE}
dataSet <- data %>% filter(brand != "No Response") %>% droplevels()
```

## Age and salary are discretized
```{r, echo=FALSE}
dataSet$ageCat <- cut(dataSet$age, 
                      breaks=c(-Inf, 40, 60, Inf), 
                      labels=c("young","adult","old"))
dataSet$salCat <- cut(dataSet$salary,
                      breaks = c(-Inf, 63333.33, 106666.67, Inf),
                      labels = c("low", "middle","high"))
summary(dataSet)
```

```{r, echo=FALSE}
cor(dataSet[, c("salary","age","credit")])
```

## Comparing some features with and without NA's
```{r table, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
require(kableExtra)

dt <- data.frame(rbind(
  salary = c(19583, 161748, 87244, 20000, 150000, 84969),
  age    = c(20   ,   80  ,   50 ,  20  ,   80  ,   50),
  credit = c(423.7,  849.0, 638.9, 423.7,  849.0,  635.5)))
colnames(dt) <- c("Min", "Max", "Median", "Min", "Max", "Median")

kable(dt) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  add_header_above(c(" " = 1, "With 'No Response'" = 3, "Without 'No Response'" = 3))
```

# Distributions of the variables

## Brand effect

### Age
```{r, message=FALSE, echo=FALSE}
ggplot(dataSet, aes(age, fill = brand)) + geom_histogram() + facet_grid(. ~ brand)
```

```{r, echo=FALSE}
ggplot(dataSet, aes(ageCat, fill = brand)) + geom_bar(position = "dodge")
```

```{r, echo=FALSE}
ggplot(dataSet, aes(elevel, age, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```

```{r, echo=FALSE}
ggplot(dataSet, aes(zipcode, age, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```

```{r, echo=FALSE}
ggplot(dataSet, aes(car, age, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```

### Salary
```{r, echo=FALSE}
p <- ggplot(dataSet, aes(salary, credit, color = brand)) + geom_point()
ggExtra::ggMarginal(p, type = "histogram")
```

```{r, message=FALSE, echo=FALSE}
ggplot(dataSet, aes(salary, fill = brand)) + geom_histogram() + facet_grid(. ~ brand)
```

```{r, echo=FALSE}
ggplot(dataSet, aes(salCat, fill = brand)) + geom_bar(position = "dodge")
```

```{r, echo=FALSE}
ggplot(dataSet, aes(elevel, salary, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```

```{r, echo=FALSE}
ggplot(dataSet, aes(zipcode, salary, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```

```{r, echo=FALSE}
ggplot(dataSet, aes(car, salary, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```

### Credit
```{r, message=FALSE, echo=FALSE}
ggplot(dataSet, aes(credit, fill = brand)) + geom_histogram() + facet_grid(. ~ brand)
```

```{r, echo=FALSE}
ggplot(dataSet, aes(elevel, credit, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```


```{r, echo=FALSE}
ggplot(dataSet, aes(zipcode, credit, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```

```{r, echo=FALSE}
ggplot(dataSet, aes(car, credit, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```

## Education level effect

```{r, message=FALSE, echo=FALSE}
ggplot(dataSet, aes(age, fill = elevel)) + geom_histogram() + facet_grid(. ~ elevel)
```

```{r, message=FALSE, echo=FALSE}
ggplot(dataSet, aes(ageCat, fill = elevel)) + geom_bar(position = "dodge")
```

```{r, message=FALSE, echo=FALSE}
ggplot(dataSet, aes(salary, fill = elevel)) + geom_histogram() + facet_grid(. ~ elevel)
```

```{r, message=FALSE, echo=FALSE}
ggplot(dataSet, aes(salCat, fill = elevel)) + geom_bar(position = "dodge")
```

```{r, echo=FALSE}
p <- ggplot(dataSet, aes(salary, credit, color = elevel)) + geom_point()
ggExtra::ggMarginal(p, type = "histogram")
```

```{r, echo=FALSE}
ggplot(dataSet, aes(zipcode, salary, color = elevel)) + geom_boxplot() + facet_grid(. ~ elevel)
```

```{r, echo=FALSE}
ggplot(dataSet, aes(zipcode, credit, color = elevel)) + geom_boxplot() + facet_grid(. ~ elevel)
```

```{r, echo=FALSE}
ggplot(dataSet, aes(car, salary, color = elevel)) + geom_boxplot() + facet_grid(. ~ elevel)
```

```{r, echo=FALSE}
ggplot(dataSet, aes(car, credit, color = elevel)) + geom_boxplot() + facet_grid(. ~ elevel)
```

## Models
H: higher education level and age, higher salary
```{r, echo=FALSE}
model <- lm(salary ~ age + elevel, data = dataSet)

summary(model)
```

```{r, echo=FALSE}
ggplot(dataSet, aes(age, salary, color = brand)) + geom_point() + facet_grid(. ~ brand+ elevel)
```

H: higher salary, higher credit
```{r, echo=FALSE}
model <- lm(credit ~ salary, data = dataSet)

summary(model)
```

# Conclusion

Age and salary are uniformly distributed and credit is normally distributed. Salary and credit have a high correlation (rho = 0.795). They are also correlated with education level, that is, people with a high level of education receive high salary and credit in banks and people with a low level of education receive low salary and credit. Car models 11 are generally more common with people with higher incomes, and car models 18 and 15 with people with lower incomes.

There are more people at educational level 2, followed by level 3, level 1 and, finally, level 4. Age at educational level is equally distributed.

Older people and people with intermediate income are associated with the Belkin brand and younger people and people with low or high income are associated with the Elago brand.

