---
title: "Report"
author: "Murilo Miranda"
date: "1/30/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
```

# Look at the raw data. 
The data has empty values and semicolon is used to separated into different columns. I used read.csv2 function because the separator character is the semicolon,but I could use read.csv and change the sep-argument to ";". To solve the problem with empty values, I used na.strings argument and gave as values empty value and single space. Now, when read.csv2 sees empty or single space it counts as missing values.

```{r}
data <- read.csv2("surveyBelkinElago.csv", na.strings = c("", " "))
head(data)
```


# Check data types & missing values. 
Think about what each variable’s data type should be and make the appropriate changes. Spot missing values: are they missing at random?

# Visualise the distributions of the variables. 
Are they how you expected them to be? Can you spot any outliers?

# Explore relationships between variables. 
Correlation matrices will give you a quick overview of linear relationships between numeric variables, but you might miss non-linear relationships. Scatter-plots are the most granular visualisations: use them whenever you can! Play with other visualisations for categorical variables.

# Formulate questions and build plots that answer them. 
Build a narrative out of your findings
