---
title: 'Belkin vs. Elago: Exploratory Data Analysis'
author: "Murilo Miranda"
date: "`r format(Sys.Date(), "%Y-%B-%d")`"
output:
  html_document:
    df_print: paged
  pdf_document: default
version: '0.1'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
```

# Look at the raw data
The data has empty values and semicolon is used to separated into different columns. I used read.csv2 function because the separator character is the semicolon,but I could use read.csv and change the sep-argument to ";". To solve the problem with empty values, I used na.strings argument and gave as values empty value and single space. Now, when read.csv2 sees empty or single space it counts as missing values.

```{r}
data <- read.csv2("surveyBelkinElago.csv", na.strings = c("", " "))
head(data)
```


### Check data types & missing values
I think elevel, car and zipcode are factors, so I converted them. There are 5000 missing values in the brand feature.

```{r}
str(data)
```

### Convert data types
```{r}
data$elevel <- as.factor(data$elevel)
data$car <- as.factor(data$car)
data$zipcode <- as.factor(data$zipcode)
summary(data)
```

### Check duplicate observations
```{r}
anyDuplicated(data)
```

### Check correlation between numeric features
```{r}
cor(data[, c("salary","age","credit")])
```

### Are missing values at random?
A method I use is a shadow matrix, in which the dataset consists of indicator features where a 0 is given if a value is present, and 1 if it isn't. Correlating these with each other and the original data can help determine if features tend to be missing together (missing at random - MAR) or not (missing completely at random - MCAR). 

```{r}
# Elements of x are 1 if a value in the data is missing and 0 if non-missing.
x <- as.data.frame(abs(is.na(data)))

# Extracting features that have some missing values.
y <- x[which(sapply(x, sd) > 0)]
```

I selected the features with numerical values, then their correlations were verified.
```{r}
cor(data[, c("salary","age","credit")], y, use="pairwise.complete.obs")
```

```{r, echo=FALSE}
rm(x, y)
```

The correlations shows that they are missing at random.

# Visualise the distributions of the variables

```{r, message=FALSE}
ggplot(data, aes(age)) + geom_histogram()
```

```{r}
p <- ggplot(data, aes(salary, credit)) + geom_point()
ggExtra::ggMarginal(p, type = "histogram")
```

```{r}
ggplot(data, aes(elevel, salary)) + geom_boxplot()
```

```{r}
ggplot(data, aes(elevel, credit)) + geom_boxplot()
```

```{r}
ggplot(data, aes(zipcode, salary)) + geom_boxplot()
```

```{r}
ggplot(data, aes(zipcode, credit)) + geom_boxplot()
```

```{r}
ggplot(data, aes(car, salary)) + geom_boxplot()
```

```{r}
ggplot(data, aes(car, credit)) + geom_boxplot()
```

# Remove NA's in brand feature
```{r}
#Drops any rows with missing values and omits them forever
dataSet <- na.omit(data)
```

### Age and salary are discretized
```{r}
dataSet$ageCat <- cut(dataSet$age, 
                      breaks=c(-Inf, 40, 60, Inf), 
                      labels=c("young","adult","old"))
dataSet$salCat <- cut(dataSet$salary,
                      breaks = c(-Inf, 63333.33, 106666.67, Inf),
                      labels = c("low", "middle","high"))
summary(dataSet)
```

```{r}
cor(dataSet[, c("salary","age","credit")])
```

### Comparing some features with and without NA's
```{r table, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
require(kableExtra)

dt <- data.frame(rbind(
  salary = c(19583, 161748, 87244, 20000, 150000, 84969),
  age    = c(20   ,   80  ,   50 ,  20  ,   80  ,   50),
  credit = c(423.7,  849.0, 638.9, 423.7,  849.0,  635.5)))
colnames(dt) <- c("Min", "Max", "Median", "Min", "Max", "Median")

kable(dt) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  add_header_above(c(" " = 1, "With NA's" = 3, "Without NA's" = 3))
```

# Visualise the distributions of the variables

## Brand effect

### Age
```{r, message=FALSE}
ggplot(dataSet, aes(age, fill = brand)) + geom_histogram() + facet_grid(. ~ brand)
```

```{r}
ggplot(dataSet, aes(ageCat, fill = brand)) + geom_bar(position = "dodge")
```

```{r}
ggplot(dataSet, aes(elevel, age, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```

```{r}
ggplot(dataSet, aes(zipcode, age, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```

```{r}
ggplot(dataSet, aes(car, age, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```

### Salary
```{r}
p <- ggplot(dataSet, aes(salary, credit, color = brand)) + geom_point()
ggExtra::ggMarginal(p, type = "histogram")
```

```{r, message=FALSE}
ggplot(dataSet, aes(salary, fill = brand)) + geom_histogram() + facet_grid(. ~ brand)
```

```{r}
ggplot(dataSet, aes(salCat, fill = brand)) + geom_bar(position = "dodge")
```

```{r}
ggplot(dataSet, aes(elevel, salary, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```

```{r}
ggplot(dataSet, aes(zipcode, salary, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```

```{r}
ggplot(dataSet, aes(car, salary, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```

### Credit
```{r, message=FALSE}
ggplot(dataSet, aes(credit, fill = brand)) + geom_histogram() + facet_grid(. ~ brand)
```

```{r}
ggplot(dataSet, aes(elevel, credit, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```


```{r}
ggplot(dataSet, aes(zipcode, credit, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```

```{r}
ggplot(dataSet, aes(car, credit, color = brand)) + geom_boxplot() + facet_grid(. ~ brand)
```

## Education level effect

```{r, message=FALSE}
ggplot(dataSet, aes(age, fill = elevel)) + geom_histogram() + facet_grid(. ~ elevel)
```

```{r, message=FALSE}
ggplot(dataSet, aes(ageCat, fill = elevel)) + geom_bar(position = "dodge")
```

```{r, message=FALSE}
ggplot(dataSet, aes(salary, fill = elevel)) + geom_histogram() + facet_grid(. ~ elevel)
```

```{r, message=FALSE}
ggplot(dataSet, aes(salCat, fill = elevel)) + geom_bar(position = "dodge")
```

```{r}
p <- ggplot(dataSet, aes(salary, credit, color = elevel)) + geom_point()
ggExtra::ggMarginal(p, type = "histogram")
```

```{r}
ggplot(dataSet, aes(zipcode, salary, color = elevel)) + geom_boxplot() + facet_grid(. ~ elevel)
```

```{r}
ggplot(dataSet, aes(zipcode, credit, color = elevel)) + geom_boxplot() + facet_grid(. ~ elevel)
```

```{r}
ggplot(dataSet, aes(car, salary, color = elevel)) + geom_boxplot() + facet_grid(. ~ elevel)
```

```{r}
ggplot(dataSet, aes(car, credit, color = elevel)) + geom_boxplot() + facet_grid(. ~ elevel)
```

## Models
H: higher education level and age, higher salary
```{r}
model <- lm(salary ~ age + elevel, data = dataSet)

summary(model)
```

```{r}
ggplot(dataSet, aes(age, salary, color = brand)) + geom_point() + facet_grid(. ~ brand+ elevel)
```

H: higher salary, higher credit
```{r}
model <- lm(credit ~ salary, data = dataSet)

summary(model)
```